\section{Einleitung}

In diesem Kapitel wird auf die grundsätzlichen Probleme durch fehlende Sicherheit und einen fehlerhaften Schutz privater Daten die in einer Cloud gespeichert werden eingegangen.



\subsection{Szenario}


\subsection{Probleme durch fehlerhaften Schutz in der Cloud}
The threat of account and service hijacking is real in cloud computing. Attackers or hackers still pose the threat of gainingunauthorized and malicious entry into a web service in a website hosted in a cloud server or whose service providers rely on cloudcomputing. Hackers still  have  great  powers  to  install their  control  software  in  cloud  infrastructures.  Since  future  generations  will be  increasingly  reliant on cloud computing, it means that plentiful more data (personal and private) will require to be dealt with through cloud computing and hence the need to address service hijacking and many other security issues. Abuse and malicious use of cloud computing is also a major challenge going into the future. Hackers can install malware and spam to gain access and commit fraud and theft. In the same category are cross-site scripting, denial of service attacks and insecure programming of applications. Additionally, data breaches, hacked interfaces, and APIs, broken authentications and compromised credentials are also con-cerns for many peopleThere are a number of challenges in cloud computing that are related to performance. These include longer downtime and reduced service provider reliability. When companies are reliant on crowded cloud computing providers, they risk facing lengthy and loss-ridden down-times  for  which  they  have  little  control  over \cite{Jabbar2020}

\subsection{Probleme durch fehlende Sicherheit in der Cloud}

\cite{inproceedings}

\cite{article}

\cite{patent}

\cite{book}

\cite{electronic}